Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

>>>>

#Filter out low-prevalance phyla
  #1. Define phyla to filter
filterPhyla = c("p__Caldiserica", "p__Deferribacteres", "p__LD1", "p__MVP-21", "p__OctSpA1-106", "p__TPD-58", "p__SC4", "p__VHS-B3-43", "p__WS1" )
  #2. Filter entries
github_filtered = subset_taxa(githubdata_phyloseq, !Phylum %in% filterPhyla)
github_filtered
  #3. Create data frame in R Markdown for easier comparison (see prevdf)
prevdf_filtered = apply(X = otu_table(github_filtered),
               MARGIN = ifelse(taxa_are_rows(github_filtered), yes = 1, no = 2),
               FUN = function(x){sum(x > 0)})

prevdf_filtered = data.frame(Prevalence = prevdf_filtered,
                    TotalAbundance = taxa_sums(github_filtered),
                    tax_table(github_filtered))

plyr::ddply(prevdf_filtered, "Phylum", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})
